Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2020-12-20 GWLDCII.tex
finished going through the referee comments

By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also show that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}. \todo{check tenses throughout (M.24) -- maybe past is better, see the ``had'' at the beginning of the next paragraph, can we discuss?}

@@

Thus we have shown that Algorithm \ref{alg:put GN on WLD} does in fact produce a Grassmann necklace. Next we check that it produces the correct one, i.e. the Grassmann necklace that defines $M(W)$. 
\begin{thm}\label{res alg gives correct GN} 
The Grassmann necklace $(I_1 \ldots I_n)$ from Theorem~\ref{res:alg gives GN} is the Grassmann necklace of the positroid $M(W)$.
\end{thm}
\begin{proof}
We have shown in the previous theorem that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$. Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show the following points.
\begin{itemize}
\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$ (for any $i \in [n]$) then $J$ is not a basis for $M(W)$. 
\end{itemize}
The first point follows immediately.  The algorithm assigns each propagator to a vertex in the support of that propagator, so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.

@@

On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and we must have ${I_{n-2}^V(q) = I_{n-2}^W(q) = n-2}$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$). If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.

@@

The next several lemmas assume $V$ and $W$ to be as above. These lemmas discuss how the shape of the Le diagram changes from $V$ to $W$ and how the plusses in $V$ shift to become plusses in $W$. In particular, the Le diagram for $W$ has an extra row, labeled by $n-3$, with three columns (see Figure~\ref{fig Le} and Lemma~\ref{lem shape}). This last row contains three (new) plusses. All other plusses in the Le diagram of $V$ shift in a predictable manner to become plusses in the Le diagram of $W$; this is described in Lemma ~\ref{lem n and n-1} to Theorem~\ref{thm dim}.

@@

\begin{proof}
Recall that $I_1^W = I_1^V\cup \{n-3\}$ and that $n-2,n-1,n \not\in I_1^W$.

@@

 The pairing is defined as follows:
  \begin{itemize}
  \item The plusses in the $\mathcal{B}$ region of both Le diagrams are identical, so each plus in this region is paired with itself.
  \item Every square containing a plus in the leftmost two columns (the $n^{th}$ and the $(n-1)^{th}$ columns) \todo{generally turn $n$ to $n^{th}$ throughout M.60} of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
  \item The plusses in the $n-3$ column for $V$ are paired with the corresponding plusses in the $n-2$ column for $W$.
  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus in this column. If $n-4 \not\in I_1^V$ then pair this plus with the $(n-5)\rightarrow (n-1)$ plus in $W$, whereas if $n-4 \in I_1^V$ then pair it with the $(n-5) \rightarrow n$ plus in $W$.

@@

\begin{eg}
Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $r$ to rows $1,2,3$ respectively, we obtain the matrix
\[
C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}.
\]
The Grassmann necklace of this diagram \hlfix{is}{M.65 wants to replace with "consists of". I disagree} 
\begin{gather*}I_1 = \{1,2,4\},\ I_2 = \{2,4,5\},\ I_3 = \{4,5,6\},\ I_4=\{4,5,6\},\\ I_5=\{5,6,7\},\ I_6 = \{6,7,1\},\ I_7=\{7,1,2\}. \end{gather*}  
Figure~\ref{fig R eg} indicates which vertex is contributed to $I_i$ by each propagator, for each $i \in [1,7]$.

>>>>

By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also show that $M(W)$ is a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}. \todo{check tenses throughout (M.24) -- maybe past is better, see the ``had'' at the beginning of the next paragraph, can we discuss?}

@@

Thus we have shown that Algorithm \ref{alg:put GN on WLD} does produce a Grassmann necklace. Next we check that it produces the correct one, i.e. the Grassmann necklace that defines $M(W)$. 
\begin{thm}\label{res alg gives correct GN} 
The Grassmann necklace $(I_1 \ldots I_n)$ from Theorem~\ref{res:alg gives GN} is the Grassmann necklace of the positroid $M(W)$.
\end{thm}
\begin{proof}
We have shown in the previous theorem that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$. Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show the following points.
\begin{itemize}
\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$ (for any $i \in [n]$) then $J$ is not a basis for $M(W)$. 
\end{itemize}
The first point follows immediately.  The algorithm assigns each propagator to a vertex in the support of that propagator, so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.

@@

On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and we must have ${I_{n-2}^V(q) = I_{n-2}^W(q) = n-2}$ since $q$ is always the clockwise-most propagator supported on vertex $n-2$. If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.

@@

The next several lemmas assume $V$ and $W$ to be as above. These lemmas discuss how the shape of the Le diagram changes from $V$ to $W$ and how the plusses in $V$ shift to become plusses in $W$. In particular, the Le diagram for $W$ has an extra row, labeled by $n-3$, with three columns (see Figure~\ref{fig Le} and Lemma~\ref{lem shape}). This last row contains three (new) plusses. All other plusses in the Le diagram of $V$ shift in a predictable manner to become plusses in the Le diagram of $W$; this is described in Lemma~\ref{lem n and n-1} to Theorem~\ref{thm dim}.

@@

\begin{proof}
Recall that $I_1^W = I_1^V\cup \{n-3\}$ and that $n-2$, $n-1$, and $n$ are not in $I_1^W$.

@@

 The pairing is defined as follows:
  \begin{itemize}
  \item The plusses in the $\mathcal{B}$ region of both Le diagrams are identical, so each plus in this region is paired with itself.
  \item Every square containing a plus in the leftmost two columns (the $n^{th}$ and the $(n-1)^{th}$ columns) \todo{generally turn $n$ to $n^{th}$ throughout M.60 -- I disagree and for reasons I can articulate} of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
  \item The plusses in the $n-3$ column for $V$ are paired with the corresponding plusses in the $n-2$ column for $W$.
  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus in this column. If $n-4 \not\in I_1^V$ then pair this plus with the $(n-5)\rightarrow (n-1)$ plus in $W$, whereas if $n-4 \in I_1^V$ then pair it with the $(n-5) \rightarrow n$ plus in $W$.

@@

\begin{eg}
Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $r$ to rows $1,2,3$ respectively, we obtain the matrix
\[
C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}.
\]
The Grassmann necklace of this diagram \hlfix{is}{M.65 wants to replace with "consists of". I disagree -- let's discuss} 
\begin{gather*}I_1 = \{1,2,4\},\ I_2 = \{2,4,5\},\ I_3 = \{4,5,6\},\ I_4=\{4,5,6\},\\ I_5=\{5,6,7\},\ I_6 = \{6,7,1\},\ I_7=\{7,1,2\}. \end{gather*}  
Figure~\ref{fig R eg} indicates which vertex is contributed to $I_i$ by each propagator, for each $i \in [1,7]$.
